\documentclass[12pt]{article}
\usepackage{fullpage}
\usepackage{amssymb,amsmath}

\newtheorem{theorem}{Theorem}

 \newcommand{\Header}[1]{\begin{center} {\Large\bf #1} \end{center}}
 \newcommand{\header}[1]{\begin{center} {\large\bf #1} \end{center}}
\setlength{\parindent}{0.0in}
\setlength{\parskip}{1ex}


%\newif\ifnotes\notestrue
\newif\ifnotes\notesfalse


\input{../com440-default.tex}
\input{../com440-macros.tex}


\begin{document}
\header{COM-440, Introduction to Quantum Cryptography, Fall 2025}
{\bf Homework \# 2} \hfill {\bf due: 12:59PM, {\color{blue}October 19th}, 2025}


\medskip

\hrule

\medskip 

Ground rules: 

{\bf Please
  format your solutions so that each problem begins on a new page, and
  so that your name appears at the top of each page.}

You are encouraged to collaborate with your classmates on
homework problems, but each person must write up the final solutions
individually. You should note on your homework specifically which
problems were a collaborative effort and with whom. You may not search
online for solutions, but if you do use research papers or other
sources in your solutions, you must cite them. If you use an AI tool to 
partially solve a question, or improve your write-up of a solution, then 
you should also mention it. All questions on the homework, including requests for clarifications or typos, should be directed to the Ed forum.

Late homework will not be accepted or graded. Extensions will not be granted, except on the recommendation of an academic committee. 

Each of the four problem set counts for 20\% of the total homework grade. (Each of the two readings will count for 10\% of the final homework grade.)


\medskip

\hrule

\medskip


Revisions since the first posting are in \textcolor{blue}{blue}.

{\bf Problems:}
\begin{enumerate}



\item (4 points) \textbf{A Guessing Game.}\\
Imagine that Alice and Eve play a guessing game where they share a two-qubit state \(\rho_{AE}\). First, Alice produces a random bit \(\theta\in\{0,1\}\), and she measures her qubit in the standard basis if \(\theta=0\) and in the Hadamard basis if \(\theta=1\). In both cases she obtains a bit \(x\in\{0,1\}\) as measurement outcome. She then announces \(\theta\) to Eve. Eve's goal is to guess the bit \(x\). Imagine that \(\rho_{AE} = |\mathrm{EPR}\rangle\langle\mathrm{EPR}|\), where as usual $\ket{\mathrm{EPR}} = \frac{1}{\sqrt{2}}(\ket{00}+\ket{11})$, so Alice and Eve share a maximally entangled pair of qubits. In this scenario we know that if Eve measures in the same basis as Alice she will get the same outcome and  thus be able to guess \(x\) perfectly.
\begin{enumerate}
\item Suppose now that Alice wants to foil Eve so, before measuring, she first applies some unitary \(U_A\) to her qubit, and then measures. Of course Eve, being really smart, gets wind of this so she will know what unitary Alice has used before measuring. So they share the state\\
\[|\Phi_U\rangle = (U_A\otimes \mathbf{1}_E)\frac{1}{\sqrt{2}}(\ket{00}+ \ket{11})\]
and Eve knows \(\theta\) and \(U_A\). In this scenario, what is Eve's optimal guessing probability, and what is a strategy that achieves it? 
\item Consider now a scenario in which Alice's strategy consists in choosing one out of three possible unitaries, according to a distribution that may depend on her choice of $\theta$. The three unitaries are the same whether $\theta=0$ or $\theta=1$, and Eve knows what they are as well as the distribution used by Alice, but she does not learn which unitary Alice eventually selected. Provide a set of three unitaries that makes Eve's guessing probability the lowest possible. (You do not need to prove that your strategy is optimal.)
\item Suppose we restrict Alice's set of possible unitaries to contain only two. Can she still make Eve's guessing probability as low as in part (b)?
\end{enumerate}



\item {(6 points)} {\bf Robustness of GHZ and W States, Part II.}\\
We return to the multi-qubit GHZ and W states introduced in the previous exercise. 
In class we learned to distinguish product states from (pure) entangled states by calculating the Schmidt rank of $\ket{\Psi}_{AB}$, i.e. the rank of the reduced state $\rho_A=\Tr_B \ketbra{\Psi}{\Psi}$. In particular $\rho$ is pure if and only if $\ket{\Psi}$ has Schmidt rank 1. In the following, we denote by $\Tr_N$ the operation of tracing out only the last one out of $N$ qubits.
\begin{enumerate}
\item What are the ranks $r_{GHZ}$ of $\Tr_N \ketbra{GHZ_N}{GHZ_N}$ and $r_W$ of $\Tr_N \ketbra{W_N}{W_N}$, respectively? (Note that these are the Schmidt ranks of $\ket{GHZ_N}$ and $\ket{W_N}$ if we partition each of them between the first $N-1$ qubits and the last qubit.)
%\solopen{By direct calculation we have $$\Tr_N \proj{GHZ_N} = \frac{1}{2}\proj{0}^{\otimes {N-1}}+\frac{1}{2}\proj{1}^{\otimes {N-1}}$$ and $$\Tr_ N \proj{W_N} = \frac{N-1}{N}\proj{W_{N-1}}+\frac{1}{N}\proj{0}^{\otimes {N-1}}.$$ Both of which are diagonal (in some basis) and have rank 2. Note that this is also the \emph{highest} rank one can get when tracing out a single qubit, as $\rho_A=\rho_B$.}
%
\end{enumerate}
 Let us now introduce a more discriminating (in fact, continuous) measure of the entanglement of a state $\ket{\Psi}_{AB}$: namely, the \textit{purity} of the reduced state $\rho_A$ given by $\Tr \rho_A^2 $. First let's see how this works in practice with the extreme cases in $d$ dimensions:
\begin{enumerate}
\item[(b)] What are the purities $\Tr \left(\rho^2\right)$ for $\rho=\ketbra{0}{0}$ and the ''maximally mixed'' state $\rho=\frac{1}{d} \id_d$, respectively?
%\solopen{For $\rho =\proj{0}$ we have $\rho^2=\rho$ and thus $\Tr\left(\rho^2\right)=1$. On the other hand, for $\rho =\frac{1}{d} \id_d$ we have $\rho^2=\frac{1}{d^2} \id_ d$ from which it follows that $\Tr \left(\rho^2\right)=\frac{1}{d}$}
% \begin{enumerate}[a)]
% 	\item 1 and 0
% 	\item 1 and $\frac{1}{d}$
% 	\item 1 and $\frac{1}{d^2}$
% 	\item $\frac{1}{d}$ and $\frac{1}{d^2}$
% \end{enumerate}
%
\item[(c)] Is the purity of $\rho_A$ higher or lower for more entangled states $\ket{\Psi}_{AB}$? Can you explain this in terms of the definition $\Tr \left(\rho_A^2\right) $?
%\solopen{The extremes (pure and maximally mixed) that you considered in Problem 2.2 certainly suggest this. Informally, the more entangled $A$ and $B$ are, the more classical uncertainty you have-the more information you lose-in the state $\rho _ A$ of $A$ alone after tracing out $B$. This expresses itself as a lower purity as defined above.}
\end{enumerate}
Now consider again the behavior of the $N$-qubit GHZ and W states with one qubit discarded (i.e. traced out):
\begin{enumerate}
\item[(d)] What is the purity of $\Tr_N \ketbra{GHZ_N}{GHZ_N}$ in the limit $N \rightarrow \infty$?
%\solopen{Again we have by direct calculation $$\rho = \Tr_ N \proj{GHZ_N} = \frac{1}{2}\proj{0}^{\otimes {N-1}}+\frac{1}{2}\proj{1}^{\otimes {N-1}}$$ from which it follows that $$\rho^2 = \frac{1}{4}\proj{0}^{\otimes {N-1}}+\frac{1}{4}\proj{1}^{\otimes {N-1}}$$ and $\Tr \left(\rho^2\right)=\frac{1}{2}$ for all $N$.}
% \begin{enumerate}[a)]
% 	\item 0
% 	\item $1/N$
% 	\item 1/2
% 	\item 1
% \end{enumerate}
%
\item[(e)] What is the purity of $\Tr_N \ketbra{W_N}{W_N}$ in the limit $N \rightarrow \infty$?
%\solopen{We have again by direct calculation
%$$\rho = \Tr_N \proj{W_N} = \frac{N-1}{N}\proj{W_{N-1}}+\frac{1}{N}\proj{0}^{\otimes {N-1}}$$ from which it follows that $$\rho ^2 = \frac{(N-1)^2}{N^2}\proj{W_{N-1}}+\frac{1}{N^2}\proj{0}^{\otimes {N-1}}$$ and $\Tr \rho ^2 = \frac{N^2-2N+2}{N^2} \rightarrow 1$ as $N \rightarrow \infty$.}
% \begin{enumerate}[a)]
% 	\item 0
% 	\item $1/N$
% 	\item 1/2
% 	\item 1
% \end{enumerate}
\end{enumerate}
Discuss the implications for the ``robustness'' of multipartite entanglement under loss of one qubit in GHZ versus W states. What can we say about losses of more than one qubit?


\item  {\bf An optimal attack}\label{ex:opt-wiesner}\\
Let 
\[ N_1 = \frac{1}{\sqrt{12}} \begin{pmatrix} 3 & 0 \\ 0 & 1 \\ 0 & 1 \\ 1 & 0 \end{pmatrix} \quad \text{and}\quad N_2 = \frac{1}{\sqrt{12}} \begin{pmatrix} 0 & 1 \\ 1 & 0 \\ 1 & 0 \\ 0 & 3\end{pmatrix}\;.\]
\begin{enumerate}
\item Show that $(N_1,N_2)$ are valid Kraus operators in the definition of a quantum channel $\mathcal{N}(\rho)=N_1\rho N_1^\dagger + N_2 \rho N_2^\dagger$ mapping one qubit to two qubits. 
\item Show that using $\mathcal{N}$, a quantum adversary succeeds in the CLONE security game for Wiesner's quantum money scheme with probability $\frac{3}{4}$. 
\end{enumerate}




\item \textbf{Optimal qubit strategies in the CHSH game.}\\
\emph{This problem is a little harder. It will be graded, but it is ok if you are not able to complete it. You should still read it, as the result of the problem is used in the following problem.}\\
The goal of this problem is to evaluate the maximum success probability that can be achieved in the CHSH game by players sharing a two-qubit entangled state of the form 
\begin{equation}\label{eq:psitheta}
\ket{\psi_\theta}_{AB} = \cos(\theta) \ket{0}_A\ket{0}_A + \sin(\theta)\ket{1}_A\ket{1}_B,
\end{equation}
where $\theta \in [0,\pi/4]$ (other values of $\theta$ can be reduced to this case by simple change of basis or phase flip). 
 Having fixed the state, what are the optimal measurements for the players, and what is their success probability? 

We will assume the players each makes a basis measurement on their qubit. Recall that an observable 
 $O$ is a $2\times 2$ matrix with complex entries such that $O$ is Hermitian ($O^\dagger = O$) and squares to identity ($O^2 = \Id$). For any single-qubit basis measurement $\{\ket{u_0},\ket{u_1}\}$, there is an associated observable is $O = \ket{u_0}\bra{u_0}-\ket{u_1}\bra{u_1}$. Conversely, any observable that is not $\pm\Id$ has two non-degenerate eigenvalues $+1$ and $-1$, so we can uniquely identify it with a basis. 

To reduce the number of cases to consider we first make a few symmetry observations. 
\begin{enumerate}
\item[(a)] Let $O$ be a single-qubit observable such that $O$ is non-degenerate $(O\neq \pm \Id)$. Show that there exists real numbers $\alpha,\beta,\gamma$ such that $\alpha^2 + \beta^2 + \gamma^2 = 1$ and $O = \alpha X + \beta Y + \gamma Z$, with $X,Y,Z$ the standard Pauli matrices. 
\item[(b)] Let $\mathcal{B} = A_0\otimes B_0 + A_1\otimes B_0 + A_0\otimes B_1 - A_1 \otimes B_1$. Show that the success probability of the strategy in the CHSH game is $p_s = \frac{1}{2} + \frac{1}{4} \bra{\psi_\theta}\mathcal{B} \ket{\psi_\theta}$.
\item[(c)] Argue that for the purposes of computing the maximum success probability in the CHSH game of players using state $\ket{\psi_\theta}_{AB}$ as in~\eqref{eq:psitheta} we may without loss of generality restrict our attention to observables of the form $A_x = \cos(\alpha_x) X + \sin(\alpha_x)Y$ and $B_y =  \cos(\beta_x) X + \sin(\beta_y)Y$ for some angles $\alpha_x,\beta_y \in [0,2\pi)$. \emph{[Hint: do a rotation on the Bloch sphere.]}
\end{enumerate}
Based on the symmetry argument from the previous questions we have reduced our problem to understanding the maximum value that $\bra{\psi_\theta} \mathcal{B} \ket{\psi_\theta}$ can take, when $\ket{\psi_\theta}$ is as in~\eqref{eq:psitheta} and $\mathcal{B}$ is defined from observables $A_x,B_y$ as in (b). To understand this maximum value we compute the spectral decomposition of $\mathcal{B}$. 
\begin{enumerate}
\item[(d)] Show that $(Z\otimes \Id) \mathcal{B} (Z\otimes \Id) =  (\Id\otimes Z) \mathcal{B} (\Id\otimes Z) = -\mathcal{B}$. \emph{[Hint: use the special form of $A_x$ and $B_y$ you obtained from question (b).]}
\item[(e)] Show that $\mathcal{B}$ has a basis of eigenvectors of the form $\ket{\phi_{ab}} = e^{i\theta_{ab}} \ket{ab} + \ket{\overline{a}\overline{b}}$, where $a,b\in\{0,1\}$ and $\overline{a}=1-a$, $\overline{b}=1-b$. Note that up to local rotations this is the Bell basis. 
\item[(f)] Write $\mathcal{B}^2$ as a $4\times 4$ matrix depending on the angles $\alpha_x,\beta_y$, and show that $\Tr(\mathcal{B}^2)\leq 16$.
\item[(g)] Show that the largest success probability achievable in the CHSH game using $\ket{\psi_\theta}_{AB}$ is at most  $\frac{1}{2} + \frac{1}{4}\sqrt{1+\sin(2\theta)}$. \emph{[Hint: Decompose $\ket{\psi_\theta}$ in the eigenbasis of $\mathcal{B}$. Use (f) and the symmetries from (d) to bound the bound the success probability via the expression found in (b).]} 
\item[(h)] Give a strategy for the players which achieves this value, i.e. specify the players'  observables. 
\end{enumerate}


\item \textbf{Trading success probability for randomness in the CHSH game.}\\
The goal of this problem is to show that, if players succeed with higher and higher probability in the CHSH game then Alice's outputs in the game must contain more and more randomness. 
\begin{enumerate}
\item[(a)] Suppose that Alice and Bob play the CHSH game using a two-qubit entangled state $\ket{\psi_\theta}_{AB}$ as in~\eqref{eq:psitheta}. Let $p_\theta(a|x)$ be the probability that, in this strategy, Alice returns answer $a\in\{0,1\}$ to question $x\in\{0,1\}$. Show that $\max_{a,x} p_\theta(a|x) \leq \cos (2\theta)$. 
\item[(b)] Let $p_s = \frac{1}{2}+\frac{1}{4}I$ be the players' success probability in CHSH, where $I\in [-2,2]$. Using (g) from the previous problem, deduce from (a) that 
$$\forall a,x\in\{0,1\},\qquad p_\theta(a|x) \leq \frac{1}{2}\Big(1+\sqrt{2-\frac{I^2}{4}}\Big).$$
\item[(c)] Suppose now the players use any single-qubit strategy (not necessarily using $\ket{\psi_\theta}$). Prove a lower bound on the conditional min-entropy $\Hmin(A|X=x)$, for any $x\in \{0,1\}$, that is generated in Alice's outputs, as a function of the players' success probability in the CHSH game. 
\item[(d)] Show that the bound from (b) is tight: for any $\theta\in[0,\pi/4]$ find a strategy for the players using $\ket{\psi_\theta}$ such that $\max_{a,x} p_\theta(a|x) = \frac{1}{2}(1+\sqrt{2-I^2/4})$.
\end{enumerate}
\end{enumerate}
\end{document}






 
















