\documentclass[12pt]{article}
\usepackage{fullpage}
\usepackage{amssymb,amsmath}

\newtheorem{theorem}{Theorem}

 \newcommand{\Header}[1]{\begin{center} {\Large\bf #1} \end{center}}
 \newcommand{\header}[1]{\begin{center} {\large\bf #1} \end{center}}
\setlength{\parindent}{0.0in}
\setlength{\parskip}{1ex}


%\newif\ifnotes\notestrue
\newif\ifnotes\notesfalse


\input{../com440-default.tex}
\input{../com440-macros.tex}


\begin{document}
\header{COM-440, Introduction to Quantum Cryptography, Fall 2025}
{\bf Homework \# 3 Solutions} 


\medskip

\hrule

 
\medskip
{\bf Problems:}

\begin{enumerate}
		
 \item {\bf Information reconciliation via linear codes.}
\begin{enumerate}
\item  First note if $X_A$ and $X_B$ has only one error, then $X_A - X_B = e_i$ for some standard vector basis $e_i$ where $i$th bit is the erroneous bit. Hence $H(X_A - X_B) = v_i$ where $v_i$ is the $i$th column of $H$. But notice that all the columns of $H$ are distinct, so given $v_i$, we can deduce precisely what $i$, the index of the erroneous bit, is (this is the error estimate map).     \\

\item In the reconciliation scheme, Alice would send $HX_A$ to Bob. Bob would then calculate  $HX_B$ and then subtract to find $H(X_A - X_B)$. Using this Bob would figure out which bit to flip through the error estimate map, and then recover Alice's string. However, this won't work if more than one error is present, as in all cases, Bob will only change one bit depending on the error estimate. The probability of Alice and Bob succeeding is consequently the probability that at most one error occurs, which is $$ (1-p)^7 + 7p(1-p)^6 = (1-p)^6(1-p + 7p) = (1-p)^6(1+6p) $$  

\item The probability that a 7-bit message is transferred perfectly without any reconciliation is just $(1-p)^7$, which is $7p(1-p)^6$ smaller than if we could do a single error reconciliation as in the previous part. Using the 3-bit single error reconciliation scheme with the $H$ given in this part, we successfully transmit the 3-bit message without error with probability $$ (1-p)^3 + 3p(1-p)^2 = (1-p)^2(1-p+3p) =(1-p)^2(1+2p)$$ The leading term of all these probabilities is 1, but the linear term of the success probability of just transferring 7 bits without reconciliation, $(1-p)^7 = 1 - 7p+\dots$, is $-7$,  while the linear term of the success probability of the 3-bit scheme, $(1-p)^2(1+2p) = 1 + 0p - 3p^2 + \dots$, is 0,  and the linear term of the success probability of transferring 7 bits with reconciliation, $(1-p)^6(1+6p) = 1 + 0p - 21p^2+\dots$, is also 0. However the $p^2$ term is larger for the 3-bit scheme than the 7-bit scheme. Hence the leading order behavior in increasing order is the 7-bit transmission without reconciliation, then the 7-bit transmission with reconciliation, followed by the 3-bit transmission with reconciliation. 


Plotting these polynomials on a graphing calculator, we see that this order is preserved in the region $p\in (0,1/2)$. Hence in this region, if we were to think giving up 4 bits of communicating is worth it, the 3-bit scheme would be the best. Otherwise, the 7-bit scheme is the best.
\end{enumerate}

\item {\bf Establishing keys in the presence of a limited eavesdropper.}
\begin{enumerate}
    \item Have Alice send an $n$-bit weak key $X$ through these special classic channels to Bob. Then for each bit, Eve will obtain the bit with probability $q$, and will not with probability $1-q$ and just guess. Hence the probability Eve gets the correct bit is $q + \frac{1-q}2 = \frac{1+q}2$, and the probability Eve guesses all of the message is $P_{\text{guess}}(X|E) = \left(\frac{1+q}2\right)^n$. Consequently $$H_{\text{min}}(X|E) = -\log\left(\left(\frac{1+q}2\right)^n\right) = n(1-\log(1+q))\ge (2-\log 3)n$$ Now from our work done in class (Theorem 5.3.1 in notes), for $\eps = 10^{-5}$ and $k = n(2-\log 3)$ Alice and Bob can construct a $(k,\eps)$-weak seeded 2-universal extractor $\text{Ext}$ that takes $X$ and a random string $r\gets\{0,1\}^{2n}$, and outputs an $\eps$-secure key of size $$m := n(2-\log 3) + 2\log\eps = n(2-\log3) -10\log 10$$ Hence all Alice needs to do is create a length $2n$ random string $R$, find $\text{Ext}(X,R)$, send $R$ to Bob, and have Bob calculate $\text{Ext}(X,R)$.   
    
    
    Overall, we use the channel to first send the $n$-bit message $X$, and then the $2n$-bit random seed $R$. Hence the number of channel uses per bit of $\eps$-secure key is $$ \frac{3n}{m} = \frac{3n}{n(2-\log3) - 10\log10} = \frac{3}{2-\log 3 - 10\log10/n}$$ If we assume that Eve is the most powerful with $q = 1/2$ and if we make $n$ to be quite large for practical security purposes, we will have $$\frac{3n}m\to \frac{3}{2-\log 3}\approx 7.23$$ channel uses per bit of $10^{-5}$-strong key. 
    
    \item %We will rename $b=1024$ to save $k$ for entropy. 
    Let Alice send an $n$-bit weak key $X$ through the classical channel to Bob ($n\gg b$). We can then see that Eve can intercept any $b$ of them, and hence $P_{\text{guess}}(X|E) = 2^{b-n}$, and so $$k := H_{\text{min}}(X|E) = -\log P_{\text{guess}}(X|E) = n-b$$ Now again from class or Theorem 5.3.1, for $\eps = 10^{-10}$, Alice and Bob can construct a $(k,\eps)$-weak seeded 2-universal extractor Ext that takes $X$ and a random string $r\gets\{0,1\}_u^{2n}$ and outputs an $\eps$-secure key of size $$m = k + 2\log \eps = n - b - 20\log 10 = n-2014-20\log 10$$ Hence we can have Alice generate $R\gets \{0,1\}^{2n}$, calculate Ext$(X,R)$, send $R$ to Bob, and then have Bob also calculate Ext$(X,R)$. As a result, both Alice and Bob will have $\eps$-secure keys.
\end{enumerate}

\item {\bf Min-entropy from the matching outcomes bound}
\begin{enumerate}
\item Recall that $X$ is a single bit, the output of Alice's measurement. Therefore its min-entropy is upper-bounded by $1$. Since Eve is totally uncorrelated and Alice's local density matrix is $\frac12\Id$, $X$ is a uniform random bit with respect to Eve's point of view. That is, $\Hmin(X\mid E\Theta) = 1$.
\item We want to compute the probability that Alice and Bob obtain the same outcome. Suppose $\Theta = 0$, so that Alice and Bob both measure in the standard basis.
The expected value of the product of their measurement outcomes is $\bra{\Psi_{ABE}} Z\otimes Z \otimes I \ket{\Psi_{ABE}}$. If they make the same measurement, then the product of their measurements is $+1$. If they make different measurements, this product is $-1$.
Therefore the expectation is equal to $p_{\text{same}\mid\Theta = 0} - p_{\text{different}\mid\Theta = 0}$. These two probabilities sum to $1$, so we conclude that
\[p_{\text{same}\mid\Theta = 0} = \frac12 + \frac 12\bra{\Psi_{ABE}} Z\otimes Z \otimes I \ket{\Psi_{ABE}}.\]
Similarly,
\[p_{\text{same}\mid\Theta = 1} = \frac12 + \frac 12\bra{\Psi_{ABE}} X\otimes X \otimes I \ket{\Psi_{ABE}}.\]
Finally,
\[
p_{\text{same}} = \frac12 p_{\text{same}\mid\Theta = 0} + \frac 12 p_{\text{same}\mid\Theta = 0}
= \frac12 + \frac 14\bra{\Psi_{ABE}} X\otimes X \otimes I \ket{\Psi_{ABE}}+ \frac 14\bra{\Psi_{ABE}} Z\otimes Z \otimes I \ket{\Psi_{ABE}}.\]

Therefore, $a = b = 1/4, c = 1/2$.
\item Applying the standard basis expansion suggested in the problem, along with the identity $X = \ketbra 01 + \ketbra 10$, we can rewrite $\bra{\Psi_{ABE}} X_A\otimes X_B \otimes I_E \ket{\Psi_{ABE}}$ as
\[
\left(\bra 0_A \otimes \bra{u_0}_{BE} +\bra 1_A \otimes \bra{u_1}_{BE}\right) \left[(\ketbra01 + \ketbra10)_A\otimes X_B\otimes I_E \right]\left(\ket 0_A\otimes \ket{u_0}_{BE} +\ket 1_A \otimes \ket{u_1}_{BE}\right).
\]
Evaluating inner products simplifies this to
\[
\bra{u_0}_{BE}X_B\otimes I_E\ket{u_1}_{BE} +
\bra{u_1}_{BE}X_B\otimes I_E\ket{u_0}_{BE}.
\]
Since the two terms in the above some are complex conjugates of each other, their sum is equal to twice their real part. That is,
\[
\bra{\Psi_{ABE}} X_A\otimes X_B \otimes I_E \ket{\Psi_{ABE}}
=2\Re\bra{u_0}_{BE}X_B\otimes I_E\ket{u_1}_{BE}
=2\Re\bra{u_1}_{BE}X_B\otimes I_E\ket{u_0}_{BE}.
\]

Thus $a' = 2, b' = 0$.
\item First, observe that by part (b),
\[
 2p-1
 = \frac 12\bra{\Psi_{ABE}} X\otimes X \otimes I \ket{\Psi_{ABE}}+ \frac 12\bra{\Psi_{ABE}} Z\otimes Z \otimes I \ket{\Psi_{ABE}}.
 \]
By part (c),
\[
 2p-1
 =\Re\bra{u_0}X_B\otimes I_E\ket{u_1}
 +\Re\bra{u_0}Z_B\otimes I_E\ket{u_1}.
 \]
 By Ulhmann's theorem,
 \[
|\bra{u_0}X_B\otimes I_E\ket{u_1}| \leq F(\sigma_E^{X,0},\sigma_E^{X,1}) \text{ and }
|\bra{u_0}Z_B\otimes I_E\ket{u_1}| \leq F(\sigma_E^{Z,+},\sigma_E^{Z,-})
 \]
 Finally, notice that for any complex $z$, $\Re z \leq |z|$. Chaining and adding inequalities gives the desired inequality with $\alpha = \beta = 1$.
 \[
|2p-1| \leq  F(\sigma_E^{X,0},\sigma_E^{X,1}) +  F(\sigma_E^{Z,+},\sigma_E^{Z,-}).
 \]
 
 So $\alpha = 1, \beta = 1$.
\item Recall that from part (d) we have
\begin{equation}
2p-1 \leq F(\sigma_E^{X,0},\sigma_E^{X,1}) + F(\sigma_E^{Z,+},\sigma_E^{Z,-})
\end{equation}
Now, $D(\rho,\sigma) \leq \sqrt{1-F(\rho,\sigma)^2} \Rightarrow F(\rho,\sigma) \leq \sqrt{1-D(\rho,\sigma)^2}$. Hence, we have
\begin{equation}
2p-1 \leq \sqrt{1-D(\sigma_E^{X,0},\sigma_E^{X,1})^2} + \sqrt{1-D(\sigma_E^{Z,+},\sigma_E^{Z,-})^2}
\end{equation}
Now, from the discussion at the start of the problem, we have the following lower bound on $\Hmin (X|E)$.
\begin{equation}
\Hmin (X|E) \geq -\log \big(\frac12(\frac12+\frac12 D(\sigma_E^{X,0},\sigma_E^{X,1}) +\frac12(\frac12+\frac12 D(\sigma_E^{Z,+},\sigma_E^{Z,-}))\big) \\
\end{equation}
Simplifying the right-hand side results in
\begin{equation}
\Hmin (X|E) \geq 1 - \log \big(1 + \frac{D(\sigma_E^{X,0},\sigma_E^{X,1}) + D(\sigma_E^{Z,+},\sigma_E^{Z,-})}{2}\big)
\end{equation}
We want to find the maximum value of $D(\sigma_E^{X,0},\sigma_E^{X,1}) + D(\sigma_E^{Z,+},\sigma_E^{Z,-})$ subject to $2p-1 \leq \sqrt{1-D(\sigma_E^{X,0},\sigma_E^{X,1})^2} + \sqrt{1-D(\sigma_E^{Z,+},\sigma_E^{Z,-})^2}$.
We look at this as an optimization problem. The maximum value of $x+y$ subject to the constraint $\sqrt{1-x^2} + \sqrt{1-y^2} \geq \alpha$ is achieved when $\sqrt{1-x^2} = \sqrt{1-y^2} = \alpha/2$. Hence, we get the desired bound
\begin{equation}
\Hmin (X|E) \geq 1 - \log\big(1+\sqrt{p(1-p)+ \frac34}\,\,\big).
\end{equation}
\end{enumerate}

\end{enumerate}

\end{document}






 
















